
\documentclass[conference]{IEEEtran}

\ifCLASSINFOpdf

\else

\fi

\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{amsmath}
\usepackage{caption}


\begin{document}

\title{WEIR - Assignment 1 - Preferential web crawling}



\author{\IEEEauthorblockN{Maj Bregar, Gal Fajon, Alen Leban}

\IEEEauthorblockA{ Faculty of Computer and Information Science\\Večna pot 113, 1000 Ljubljana}
}

\maketitle

% WIP text, will be cleaned and reformatted

\begin{abstract}
In this assignment we developed a preferential web crawler for the news site 24ur.com\cite{24ur} that collects pages relevant to a user‑specified topical query (for example, the conflict between Russia and Ukraine). Relevance is estimated by embedding page metadata, such as titles, summaries, and keywords, into a vector space using a pre‑trained language model, then computing cosine similarity between the page embeddings and an embedding of the query. The crawler is comprised of an SQL database server, a RESTful API server that exposes database operations, and a client that uses browser automation to extract page content and hyperlinks and applies machine‑learning scoring to prioritize crawl targets.
\end{abstract}

\IEEEpeerreviewmaketitle

\section{Introduction}
% TODO - bolj razpiši dejansko strukturo kode (katere komponente so in kaj delajo)
% TODO - Dodaj citations za vse RELEVANT packages

This report describes the design and implementation of a preferential web crawler developed to extract pages 
relevant to a user‑specified topical query within a chosen domain. For this assignment, the chosen domain 
is the Slovenian news website 24ur.com.

The crawler comprises several components: a headless browser HTTP downloader and renderer, 
a data extractor for hyperlinks and images, a duplicate detector, a preferential URL frontier 
and a PostgreSQL database accessed via a RESTful API. The system is designed to run multiple parallel workers.

Pages are prioritised according to their relevance to a user‑specified topical query (e.g. 
the conflict between Russia and Ukraine) by embedding page metadata into a natural‑language string 
that is then converted into a vector representation using a pre‑trained language model and ranked 
using cosine similarity. The implementation also enforces canonical URLs, respects robots.txt directives 
and crawl delay constraints, and records pages, images and binary files found within the domain in 
the database.

The following sections document implementation details, parameter choices, performance evaluation, 
and visualisations of the resulting data.

\section{Methodology}
\subsection{Crawler Architecture}
The crawler is implemented as a modular system consisting of a REST API, a database, and a client service. 
The entire application is deployed using Docker Compose, with service configuration and crawling parameters defined in the docker compose configuration file.

\subsection{API Server and Database}
The REST API service is implemented using a Python Flask server. It utilizes the SQLAlchemy library to define and initialize the database 
schema in accordance with the schema provided in the assignment instructions.

The server supports configurable HTTP Basic Authentication and uses Flask’s built-in ad hoc SSL context to 
enable HTTPS, ensuring secure communication between components.

The crawler client interacts with the API using an api wrapper python module, which sends requests 
using the requests library.

% Does SQLAlchemy ensure database locking during transactions?

\subsection{Crawler client}
The crawler client uses the threading module to spawn a specified number of worker threads, 
which process URLs from a shared URL frontier. 

Once a URL is acquired, it is first validated. Then, an instance of a Selenium \cite{selenium} Firefox headless web browser is launched. 
The target page is fetched and processed, and the relevant metadata is stored in the database.  

% TODO - Bolj detajlno opiši scoring in kako deluje fronta
% TODO - Kaj je ta duplication handling?

Links found on the page are extracted, scored, and added to the frontier. This process repeats until the desired number of pages has been crawled. 
If an insertion into the database fails due to URL or content hash uniqueness constraints, the client handles the error by retrieving the pre-existing 
page and either updating it or creating a \texttt{DUPLICATE} page entry.

The crawler respects the \texttt{robots.txt} file of each domain by ignoring links disallowed by the \texttt{Disallow} directive and adhering 
to the specified crawl delay.

% - the crawler locally keeps:
%  * PQ for frontier links - 
%  * front metadata dict -  Alen what is this?
%  * allowed site urls and dict of robots.txt of sites
%- communicates with database with PUT, GET, POST requests via custom Client API
%  * if insertions to db fail because of URL or HASH uniqueness constraints the client returns an error code which we service by getting the preexisitng page and updating it or creating a DUPLICATE page

% TODO - things get really technical here, lots of terminal text, maybe we should simplify.
\subsection{Page parsing}
Each subpage is parsed using the \texttt{BeautifulSoup} module. The parser is used to extract article keywords and
link URLs to other pages (in the \texttt{href} property or \texttt{onclick} JavaScript event handler).

The \texttt{onclick} event handler is processed by extracting URL candidates with regular-expression patterns 
that detect common JavaScript redirects as well 
as embedded JSON-like fields (\texttt{Url:}, \texttt{PlaybackUrl:}); if none match, it falls back to any quoted 
\texttt{.html} substring and returns the list of candidate URLs.

When saving a page to the database, each extracted URL is canonicalized using \texttt{urllib.parse} and \texttt{tldextract}. 
Redirection links belonging to the domain \texttt{go-ctr-tracker.pub.24ur.si}
are resolved using the \texttt{redir} key in the query string, the host is reduced to the 
registrable domain (\texttt{domain.suffix}), the path is normalized 
(collapsing \texttt{.}/\texttt{..} segments and removing trailing slashes), common tracking parameters 
(UTM, \texttt{fbclid}, \texttt{gclid}, \texttt{yclid}) are removed, remaining query parameters are sorted 
deterministically, and the final URL is returned with the \texttt{https} scheme and without fragments.

Binary resources are detected by file extension (\texttt{.pdf}, \texttt{.doc}, \texttt{.docx}, \texttt{.ppt}, \texttt{.pptx}). 
For HTML pages, all outgoing \texttt{<a href>} targets are canonicalized and then checked for these extensions; matching targets 
are not added to the link frontier, but are instead stored as \texttt{page\_data} entries with \texttt{data\_type\_code} set to 
the corresponding type (\texttt{PDF}/\texttt{DOC}/\texttt{DOCX}/\texttt{PPT}/\texttt{PPTX}), de-duplicated per page.

\subsection{Preferential Crawling}
Preferential crawling is implemented by maintaining a shared in-memory URL frontier as a thread-safe priority queue. 
Each worker repeatedly removes the currently best-ranked URL, downloads the page, stores it in the database, and then extracts outgoing links.

For each discovered URL, the crawler first applies canonicalization and filters out already visited URLs, 
off-domain URLs, and URLs disallowed by \texttt{robots.txt}. The parsing stage (Section \emph{Page parsing})
associates each link with metadata such as an inferred link title (from the URL slug), an optional 
summary (from nearby \texttt{p}/\texttt{span} elements with class \texttt{summary}), page-level article 
keywords (from the \texttt{article-keywords} block), and additional keyword-like signals (URL section/topic 
and optional label text). 

Since the same URL can be encountered multiple times from different pages and 
page regions, metadata is accumulated across occurrences in a per-URL list; every time new metadata is 
appended, a per-URL \emph{version counter} is incremented.

Relevance scoring is performed with a multilingual sentence-transformer model 
(\texttt{paraphrase-multilingual-MiniLM-L12-v2} \cite{BERTmodel}). At the start of crawling 
the user query is embedded once, producing a normalized query embedding $\mathbf{e}_q$. For every 
candidate frontier URL $u$, the crawler constructs a short natural-language metadata string by 
concatenating de-duplicated fields in the form \emph{Naslovi: \dots{} Povzetki: \dots{} Klju\v{c}ne besede: \dots{}} 
and embeds it into $\mathbf{e}_u$. The relevance score is then computed as cosine similarity

\begin{equation}
s(u) = \cos(\mathbf{e}_q, \mathbf{e}_u).
\end{equation}

Candidates with no available metadata are assigned an empty metadata string and a neutral score of $0$.
Because the priority queue dequeues the smallest numeric key, 
the crawler converts similarity into a frontier priority by negation ($p(u)=-s(u)$), causing more 
relevant pages (larger $s$) to be scheduled earlier. To avoid using outdated scores, frontier entries 
carry the version number that was current when they were inserted; if a URL is encountered again and 
its metadata (and thus its version) increases, older queued entries are discarded when popped. 

In addition to the in-memory frontier, every candidate is also stored in the database as a 
\texttt{FRONTIER} page with its current priority, and a link edge is recorded from the currently 
crawled page to the corresponding frontier entry; when a frontier URL is later crawled, that database 
entry is updated with the full page content.

\subsection{Deduplication}
To avoid storing identical (or near-identical) content multiple times, every downloaded HTML page is 
assigned a content fingerprint and the database enforces uniqueness of this fingerprint. The fingerprint 
is computed using the \texttt{ppdeep} (ssdeep) fuzzy-hashing algorithm.

Before hashing, the HTML is parsed and non-content elements (\texttt{script}, \texttt{style}, \texttt{noscript}) 
are removed. If the page contains an \texttt{<article>} element, its text is used as the primary content; 
two highly dynamic sub-blocks are explicitly removed when present: the comments placeholder (\texttt{id=comments\_placeholder}) 
and a promotional widget (\texttt{data-upscore-zone=microsite\_promo}). The remaining article text is extracted, whitespace-normalized, 
and hashed. For non-article pages, a fallback signature is constructed from stable navigation/text cues, such as submenu item titles 
and page headers (e.g., \texttt{h1} elements under \texttt{pageContent}).

The resulting hash is stored in the \texttt{content\_hash} field of the \texttt{page} table, which is protected by a unique constraint 
(\texttt{unq\_hash\_idx}). When inserting or updating a page violates this constraint, the client resolves the conflict by locating the 
already-stored page with the same hash and creating a new entry marked as \texttt{DUPLICATE} (with \texttt{html\_content} cleared and the 
hash omitted to avoid re-triggering the constraint). A link is then recorded from the duplicate entry to the original page, preserving the 
crawl graph while preventing redundant storage of page bodies.

\section{Crawling Analysis}
- sites - just 24ur
- html, binary, duplicate, frontier page counts
- link count globally, avg per page
- image count globally, avg per page
- time crawling per page (different stages)


\subsection{Crawling Quality}
- include visualization of clustering
- include accuracy, precision, recall etc of our crawling (page is what we are looking for with query - TP, page is not what we are looking for with query - TN)

\subsection{24Ur.com Topography}
- visualization of link table
- maybe vis representing clusters as nodes, size of connection between nodes how many links are between those clusters?


\section{Disscussion}
- mention the fact we do not pick up many duplicates/binary files
- mention crawling quality, how we could improve it etc

\section{Conclusion}
- yap yap yap

\bibliographystyle{IEEEtran}
\bibliography{ref}

\end{document}


